The Heavy Photon Search Test Detector

### 2014-04-22 hps-testrun-nim.tex
Added new beam line figure. Fixed acceptance numbers.

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test Run apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in a final state particle within a few degrees of the incoming beam, especially at low 
$m_{\Aprime{}}$. Detectors must therefore be placed close to the beam. 
The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
they constitute a "wall of flame" which must be completely avoided. Accordingly, 
the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
interaction backgrounds. Even with these precautions, the occupancies of sensors near the beam 
plane are high, dominated by the
multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
The trigger comes from a highly-segmented  lead-tungstate (PbWO$_{4}$) crystal calorimeter located just 
downstream of the dipole magnet. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test Run detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.33\times1.33$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

@@

\section{The HPS Test Run Beamline}
The HPS Test Run studied multiple Coulomb scattering of electrons and positrons from 
bremsstrahlung photons produced in the Hall B tagged photon facility. 
Figure~\ref{fig:hpstest_layout} shows the layout of 
the setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane compared to nominal electron beam running to 
allow clean passage of the photon beam through the system. 
\begin{figure}[]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

>>>>

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test Run apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in a final state particle within a few degrees of the incoming beam, especially at low 
$m_{\Aprime{}}$. Detectors must therefore be placed close to the beam. 
The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
they constitute a "wall of flame" which must be completely avoided. Accordingly, 
the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
interaction backgrounds. Even with these precautions, the occupancies of sensors near the beam 
plane are high, dominated by the
multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
The trigger comes from a highly-segmented  lead-tungstate (PbWO$_{4}$) crystal calorimeter located just 
downstream of the dipole magnet. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test Run detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < 70$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& (5 hits) &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < 60$ & 442 & 12 & 4~ns & 1 & $1.33\times1.33$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

@@

\section{The HPS Test Run Beamline}
The HPS Test Run studied multiple Coulomb scattering of electrons and positrons from 
bremsstrahlung photons produced in the Hall B tagged photon facility. 
Figure~\ref{fig:hpstest_layout} shows the layout of 
the setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane compared to nominal electron beam running to 
allow clean passage of the photon beam through the system. 
\begin{figure}[]
%    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
    \includegraphics[width=0.45\textwidth]{figures/hps-testrun-beamline-edited2}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}
